### 2023-10-02 3.Design/genwei.tex
Finished updating genwei

Training can only be done outside of the circuit as this state of the project. However, in order to train the weights as closely as they would have been on a real circuit, the activation functions used for the training are the custom activation functions generated by the dedicated circuit (\cref{sec:af}). In other words, the activation functions used are the ones shown in \cref{fig:afGraph}. This allows to train the weights as they almost (considering the activation functions are recreated using 51 points) as they would have been in the real circuit.

All the training are done using \ac{MSE} loss function and Adam optimizer \cite{adamOpti}.

@@

Once all the parameters (number of hidden states, number of dense layers, etc) have been set. The weights can be exported using the required weight

Once a correct architecture has been found, the weights are reorganized based the same model required by the netlist generator (\cref{sec:netlist}) and saved in a file along with a quick description of the architecture used for generating those weights for an easier generation of the netlist(\cref{sec:netlist}). The files can now be taken and used to generate the netlist.

>>>>

Training can only be done outside of the circuit as this state of the project. However, in order to train the weights as closely as they would have been on a real circuit, the activation functions used for the training are the custom activation functions generated by the dedicated circuit (\cref{sec:af}). In other words, the activation functions used are the ones shown in \cref{fig:afGraph}. This allows to train the weights as they almost (considering the activation functions are recreated using 51 simulated points) as they would have been in the real circuit.

All the weight trainings are done using \ac{MSE} loss function and Adam optimizer \cite{adamOpti}.

@@

Once all the parameters (number of hidden states, number of dense layers, etc) have been set. The weights can be exported using the required weight repartition layed out in \cref{sec:netlist}. A description of the architecture is also saved along the weights. This file can now be used as the input for the netlist generator (\cref{sec:netlist}).
